---
title: "Guide comparison year to year"
output: 
  html_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# setwd("C:/Users/kobiersk/Documents/projects/directories_data_transformation")
source("C:/Users/kobiersk/Documents/projects/directories_data_transformation/load_packages.R")
library("kableExtra")
library("tidyr")
library("pander")

guide_to_select <- "Chambers Global"
current_year <- year(Sys.Date())
cutoff_year <- current_year - 3
firms_list <-
  c(
    "Baker McKenzie",
    "Dentons",
    "CMS",
    "DLA Piper",
    "Hogan Lovells",
    "Norton Rose Fulbright",
    "Clifford Chance",
    "Eversheds Sutherland"
  )


df_historical_rankings <- read.table(file = "C:/Users/kobiersk/Documents/Directories/df_final_firm.csv", 
                                     sep = ";",
                                     stringsAsFactors = F,
                                     header = T)


df_data <- df_historical_rankings %>% filter(guide_agg == guide_to_select, Year.published >= cutoff_year)

```

## Summary year to year
```{r slide 0}
temp <- df_data %>% group_by(Guide) %>% summarize(n = n())
temp %>% kable() %>% kable_styling()
```

## Total number of rankings

-----------------------------------

```{r slide1}
temp <- df_data %>% group_by(Guide, Level, Is.part.of.Dentons) %>% summarise(n = n())
temp <- tidyr::spread(temp, Guide, n) %>% arrange(desc(`Is.part.of.Dentons`))

colnames(temp) <- gsub("\\.", " ", colnames(temp))

temp %>% kable() %>% kable_styling()

```

## Firms results
```{r slide2}
temp <- df_data %>% filter(Firm.agg %in% firms_list) %>%  group_by(Firm.agg, Guide, Level) %>% summarise(n = n())
temp <- tidyr::spread(temp, Guide, n) %>% arrange(desc(Firm.agg))

colnames(temp) <- gsub("\\.", " ", colnames(temp))

temp %>% kable() %>% kable_styling()

```


## Dentons practice results


### Firm level
```{r slide 3}
temp <- df_data %>% filter(Is.part.of.Dentons == "Yes", Level == "Firm level") %>%  group_by(Dentons.practice, Guide, Level) %>% summarise(n = n())
temp <- tidyr::spread(temp, Guide, n) %>% arrange(Dentons.practice)

colnames(temp) <- gsub("\\.", " ", colnames(temp))

temp %>% kable() %>% kable_styling()
```


### Individual level
```{r slide 4}
temp <- df_data %>% filter(Is.part.of.Dentons == "Yes", Level == "Individual level") %>%  group_by(Dentons.practice, Guide, Level) %>% summarise(n = n())
temp <- tidyr::spread(temp, Guide, n) %>% arrange(Dentons.practice)

colnames(temp) <- gsub("\\.", " ", colnames(temp))

temp %>% kable() %>% kable_styling()
```


## Dentons practice results - TOP rankings


### Firm level
```{r slide 5}
temp <- df_data %>% filter(Is.part.of.Dentons == "Yes", Level == "Firm level", Is.top.ranking == "Yes") %>%  group_by(Dentons.practice, Guide, Level) %>% summarise(n = n())
temp <- tidyr::spread(temp, Guide, n) %>% arrange(Dentons.practice)

colnames(temp) <- gsub("\\.", " ", colnames(temp))

temp %>% kable() %>% kable_styling()
```
### Individual level
```{r slide 6}
temp <- df_data %>% filter(Is.part.of.Dentons == "Yes", Level == "Individual level", Is.top.ranking == "Yes") %>%  group_by(Dentons.practice, Guide, Level) %>% summarise(n = n())
temp <- tidyr::spread(temp, Guide, n) %>% arrange(Dentons.practice)

colnames(temp) <- gsub("\\.", " ", colnames(temp))

temp %>% kable() %>% kable_styling()
